\tool: A Multi-Mode BadUSB Device

### 2020-12-31 WOOT/Files/badusb.tex
add impl part, todo: three mode

\subsection{Implementation}
\noindent\hongyi{The following mode is to be further decided}\\
\outline{DETAIL of each mode}\\
\outline{Automatic Scripting Mode}\\
\outline{Remote Control Mode}\\
\outline{OCR/QR Recognition Mode}\\
The implementation of \tool\ extends several existing offensive BadUSB device including Rubber Ducky\hongyi{Add Citation} (where we implement the co-operation of HID emulation and screen streaming) and Raspberry Pi (on which we implement the capture of video stream and its processing). We implemented the QR-Code extraction agent from scratch. The complete workflow of \tool, demonstrating the interaction of all the components is presented at Fig.~\ref{fig:workflow}.

\begin{figure}[htbp]
\includegraphics[width=\linewidth]{./Figs/workflow.png}
\caption{Workflow of \tool}
\label{fig:workflow}
\end{figure}

When the victim plugs in \tool device, the USB-C hub handles all the communication between each components and the victim's device. Due to the trust-by-default feature of USB protocol, the victim's video stream will be captured. Later, the stream is either processed directly by Raspberry Pi or transmitted to the attacker through GSM/WiFi components.

With video stream the capability of original Rubbery Ducky attack is considerably expanded. For example, the attacker can directly control the victim's device and view the private data in the stream. More details is presented in the Section~\ref{sec:experiment}

>>>>

\subsection{Implementation}
\noindent\hongyi{The following mode is to be further decided}\\
\outline{DETAIL of each mode}\\
\outline{Automatic Scripting Mode}\\
\outline{Remote Control Mode}\\
\outline{OCR/QR Recognition Mode}\\
Though Rubber Ducky\cite{rubber} emulates as a HID device enabling various arbitrary execution attacks, fetching feedback from the victim is more limited. Based on this restriction several defense mechanisms were proposed  like USBCheckIn\cite{usbcheckin}\hongyi{We need more example}. These defense mechanism implemented a CAPTCHA-like\cite{captcha} procedure, which requires user to complete certain challenges when a unknown HID device is plugged in. As the Rubber Ducky is only able to emulate HID device, by no means the Rubber Ducky can obtain the content of challenge and bypass it. Our \tool, on the other hand, is capable of bypassing this type of defense. Taking advantage of USB 3.x\cite{usb31}\cite{usb32}, \tool can fetch the video stream of the victim and complete the challenge automatically or manually.

As there were various Rubber Ducky implementation available, we only focus on its core functionality and our extension. Based on this pattern, we summaries our implementation of \tool into the following modes:

\begin{itemize}
\item\textit{Scripting mode} functions like the original Rubber Ducky featuring the bypass of defense mechanism like USBCheckIn\cite{usbcheckin}
\item \textit{Remote control mode} allows attacker to take complete control of victim's device manually to perform delicate operation.
\item \textit{Privacy extraction mode} captures and identify private data from the victim and send to the attacker.
\end{itemize}

\subsubsection{Scripting Mode}
\subsubsection{Remote Control Mode}
\subsubsection{Privacy Extraction Mode}

### 2020-12-31 WOOT/Files/experiment.tex
add impl part, todo: three mode

\section{Experiment}
\label{sec:experiment}
\noindent\outline{Case Study: Sharing Power Bank}\\
\outline{Overview}\\
\outline{Attack Procedure(how to  get picture, etc.)}\\
\outline{Security Issues against APPLE/Android...etc.}\\
Overview, the experiment equipment consists of
a USB Type-C hub with HDMI and USB port,
a raspberry pi 4B with a Wi-Fi chip onboard,
a video capture card adapting HDMI signal to USB camera,
and a normal powerbank with dual outputs.

>>>>

\section{Experiment}
\label{sec:experiment}
\noindent\outline{Case Study: Sharing Power Bank}\\

\subsection{Case study: Power Bank Sharing}

Power bank sharing provides users with short term rental of power banks. A provider deploys power bank sites in the city. Then, users can rent a power bank from any of the power bank site, charge their device on the trip, return the rented power bank to another site, and pay rent online.

\yechang{site or repository? }

As an example, Brick is such a power bank sharing service provider from Sweden.

\yechang{add hyperlink or reference to Brick or Brick App on App Store/Google Play.}

\yechang{Add more example to show that it is widely used?}
It provides convenience for users, but it also brings security risks. We notice that the power bank site does not check the integrity of power banks during the rental process of the power bank, and users are hardly cautious when connecting their devices to the power bank. In some situations, a malicious user is able to modify his/her rented power bank, return it to a power bank site as normal, and its next user will unknowingly connect to this malicious power bank, which endangers the privacy of user.

\outline{Overview}\\

\subsection{Overview}

\outline{Attack Procedure(how to  get picture, etc.)}\\
\outline{Security Issues against APPLE/Android...etc.}\\
Overview, the experiment equipment consists of
a USB Type-C hub with HDMI and USB port,
a raspberry pi 4B with a Wi-Fi chip onboard,
a video capture card adapting HDMI signal to USB camera,
and a normal powerbank with dual outputs.
